---
title: "Are the effects of facial feedback on emotional feeling solely driven by demand characteristics? An experimental investigation"
author: "Nicholas A. Coles"
date: "April 13, 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Readme
Code for the study reported in 'Are the effects of facial feedback on emotional feeling solely drive n by demand characteristics? An experimental investigation' Coles et al. (under review; Psychological Science).

If using RStudio and RMarkdown (which is recommended), press Ctrl + Shift + O to see the structure of the code.

## Computational reproducibility details
To get to the data processing and analysis code, you can skip to section titled "Setup R Environment". The information below is included to facilitate computational reproducibility (see Obels, Lakens, Coles, et al, 2020, AMPPS, for more details on computational reproducibility problems in science)

### R Session Information
R version 3.5.1 (2018-07-02)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows >= 8 x64 (build 9200)

Matrix products: default

locale:
[1] LC_COLLATE=English_United States.1252  LC_CTYPE=English_United States.1252   
[3] LC_MONETARY=English_United States.1252 LC_NUMERIC=C                          
[5] LC_TIME=English_United States.1252    

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] emmeans_1.4.3.01       gridExtra_2.3          lmerTest_3.1-1        
 [4] lme4_1.1-21            rmcorr_0.3.0           coin_1.3-1            
 [7] ggpubr_0.2.4           magrittr_1.5           yarrr_0.1.5           
[10] circlize_0.4.8         BayesFactor_0.9.12-4.2 Matrix_1.2-14         
[13] coda_0.19-3            jpeg_0.1-8.1           car_3.0-5             
[16] carData_3.0-3          rcompanion_2.3.7       psych_1.8.12          
[19] forcats_0.4.0          stringr_1.4.0          dplyr_0.8.3           
[22] purrr_0.3.3            readr_1.3.1            tidyr_1.0.0           
[25] tibble_2.1.3           ggplot2_3.2.1          tidyverse_1.3.0       
[28] multcomp_1.4-13        TH.data_1.0-10         MASS_7.3-51.4         
[31] survival_2.42-3        mvtnorm_1.0-11        

loaded via a namespace (and not attached):
 [1] minqa_1.2.4         colorspace_1.4-1    ggsignif_0.6.0      ellipsis_0.3.0     
 [5] modeltools_0.2-22   rio_0.5.16          estimability_1.3    GlobalOptions_0.1.1
 [9] fs_1.3.1            rstudioapi_0.10     farver_2.0.1        MatrixModels_0.4-1 
[13] fansi_0.4.0         lubridate_1.7.4     xml2_1.2.2          codetools_0.2-15   
[17] splines_3.5.1       mnormt_1.5-5        libcoin_1.0-5       knitr_1.26         
[21] zeallot_0.1.0       jsonlite_1.6        nloptr_1.2.1        broom_0.5.2        
[25] dbplyr_1.4.2        compiler_3.5.1      httr_1.4.1          backports_1.1.5    
[29] assertthat_0.2.1    lazyeval_0.2.2      cli_2.0.0           tools_3.5.1        
[33] gtable_0.3.0        glue_1.3.1          Rcpp_1.0.3          cellranger_1.1.0   
[37] vctrs_0.2.0         nlme_3.1-137        lmtest_0.9-37       xfun_0.11          
[41] openxlsx_4.1.4      rvest_0.3.5         lifecycle_0.1.0     gtools_3.8.1       
[45] zoo_1.8-6           scales_1.1.0        hms_0.5.2           parallel_3.5.1     
[49] sandwich_2.5-1      expm_0.999-4        yaml_2.2.0          curl_4.3           
[53] pbapply_1.4-2       EMT_1.1             stringi_1.4.3       nortest_1.0-4      
[57] boot_1.3-20         zip_2.0.4           shape_1.4.4         rlang_0.4.2        
[61] pkgconfig_2.0.3     matrixStats_0.55.0  lattice_0.20-38     labeling_0.3       
[65] tidyselect_0.2.5    plyr_1.8.5          R6_2.4.1            DescTools_0.99.31  
[69] generics_0.0.2      multcompView_0.1-7  DBI_1.0.0           pillar_1.4.2       
[73] haven_2.2.0         foreign_0.8-70      withr_2.1.2         abind_1.4-5        
[77] modelr_0.1.5        crayon_1.3.4        utf8_1.1.4          grid_3.5.1         
[81] readxl_1.3.1        data.table_1.12.8   digest_0.6.23       reprex_0.3.0       
[85] xtable_1.8-4        numDeriv_2016.8-1.1 stats4_3.5.1        munsell_0.5.0

## Setup R environment
```{r message = FALSE, results = "hide"}

# clear environment

rm(list = ls())

# install (if necessary) and load packages
  # function written by stevenworthington 
  Ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
      
      if (length(new.pkg)) 
          install.packages(new.pkg, dependencies = TRUE)
      
      sapply(pkg, require, character.only = TRUE)
  }

  # vector of necessary packages
  packages <- c("tidyverse", "psych", "rcompanion", "car", 
                "ggplot2", "yarrr", "ggpubr", "coin",
                "rmcorr", "lmerTest", "gridExtra", 
                "emmeans")
  
  
  # using vector of packages, call ipak function
  Ipak(packages)
  
  # delete vestigial
  rm(packages, Ipak)
  
# allow for Type III SS
options(contrasts = c("contr.sum", "contr.poly"))
  
# turn scientific notation off
options(scipen = 999)
```

## Load data
```{r}
DF <- read.csv(file = "data/demandy19a_data_raw.csv")
```

## Clean data
Select relevant variables in the data.frame
```{r}
library(magrittr)
DF %<>%
  select(
    # happy 1
    happ1_emot_hap : happ1_emot_ann, happ1_supp_dif, happ1_supp_con,
    # happy 2
    happ2_emot_hap : happ2_emot_ann, happ2_supp_dif, happ2_supp_con, 
    # anger 1
    angr1_emot_hap : angr1_emot_ann, angr1_supp_dif, angr1_supp_con,
    # anger 2
    angr2_emot_hap : angr2_emot_ann, angr2_supp_dif, angr2_supp_con, 
    # neutral 1
    neut1_emot_hap : neut1_emot_ann, neut1_supp_dif, neut1_supp_con,
    # neutral 2
    neut2_emot_hap : neut2_emot_ann, neut2_supp_dif, neut2_supp_con,
    
    # individual differences self-reports
    indiv_gend_var, indiv_agee_var : indiv_maia_032,
    
    # experiment information
    exper_init_var, exper_ssid_var, demand,
    
    # awareness
    feedb_awar_var : heard_awar_var,
    
    # order variables
    FL_5_DO, FL_6_DO,
    
    # experimenter notes
    exper_note_var
    )
```

Rename order variables
```{r}
DF %<>%
  rename(block1.order = FL_5_DO,
         block2.order = FL_6_DO)
```

Remove blank trials and practice trials (subid's in the 900's)
```{r}
DF %<>%
  filter(!is.na(exper_ssid_var),
         exper_ssid_var < 900,
         !is.na(happ1_emot_hap))
```

For belief in facial feedback hypothesis, code -1's as NA. This -1 option was confusing for experimenters, but was supposed to be reserved for instances where they were unsure what the participant's belief was.
```{r}
DF[DF$feedb_blef_var == -1, ]$feedb_blef_var <- NA
```

### Fix subject ID entry errors
Note: these errors don't affect any of the analyses or results. But they do help me identify participants' paper records.

On 11/03 MAM accidentally assigned subect 131 the subject id '120'
```{r}
DF[DF$exper_ssid_var == 120 & 
   DF$exper_init_var == "MAM", ]$exper_ssid_var <- 131
```

On 11/17 MAM accidentally assigned subject 206 the subject id '204'
```{r}
DF[DF$exper_ssid_var == 204 & 
   DF$exper_init_var == "MAM", ]$exper_ssid_var <- 206
```

On 11/19 TKA accidentally assigned subject 222 the subject id '223'
```{r}
DF[DF$exper_ssid_var == 223 & 
   DF$exper_init_var == "TKA" &
   DF$demand == "pos", ]$exper_ssid_var <- 222
```

On 01/22 KLP accidentally assigned subject 304 the subject id '303'
```{r}
DF[DF$exper_ssid_var == 303 & 
   DF$exper_init_var == "KLP", ]$exper_ssid_var <- 304
```

### Center emotion responses at 0
```{r}
DF %<>%
  mutate_at(.vars = vars(matches("emot")),
            .funs = function(x){x - 1})
```

## Create wide- and long-format dataframes
The code creates these two seperate formats because some functions are easier to run on wide vs. long formats.

### Wide-format
```{r message = FALSE}
DF.wide <- DF  # data already in wide format
```

#### Wide-format: calculate happiness and anger ratings
```{r message = FALSE}
DF.wide %<>%
  rowwise() %>%
  mutate(# Happy pose 1 emotion ratings
         happ1.happy = mean(c(happ1_emot_hap, 
                              happ1_emot_sat, 
                              happ1_emot_enj)),
         happ1.anger = mean(c(happ1_emot_irr, 
                              happ1_emot_agg,
                              happ1_emot_ann)),

         # Angry pose 1 emotion ratings
         angr1.happy = mean(c(angr1_emot_hap, 
                              angr1_emot_sat, 
                              angr1_emot_enj)),
         angr1.anger = mean(c(angr1_emot_irr, 
                              angr1_emot_agg,
                              angr1_emot_ann)),
         
         # Neutral pose 1 emotion ratings
         neut1.happy = mean(c(neut1_emot_hap, 
                              neut1_emot_sat, 
                              neut1_emot_enj)),
         neut1.anger = mean(c(neut1_emot_irr, 
                              neut1_emot_agg,
                              neut1_emot_ann)),
         
         # Happy pose 2 emotion ratings
         happ2.happy = mean(c(happ2_emot_hap, 
                              happ2_emot_sat, 
                              happ2_emot_enj)),
         happ2.anger = mean(c(happ2_emot_irr, 
                              happ2_emot_agg,
                              happ2_emot_ann)),

         # Angry pose 2 emotion ratings
         angr2.happy = mean(c(angr2_emot_hap, 
                              angr2_emot_sat, 
                              angr2_emot_enj)),
         angr2.anger = mean(c(angr2_emot_irr, 
                              angr2_emot_agg,
                              angr2_emot_ann)),
         
         # Neutral pose 2 emotion ratings
         neut2.happy = mean(c(neut2_emot_hap, 
                              neut2_emot_sat, 
                              neut2_emot_enj)),
         neut2.anger = mean(c(neut2_emot_irr, 
                              neut2_emot_agg,
                              neut2_emot_ann)) 
         ) %>% 
  ungroup()
```

### Long-format
Transpose data from wide to long format
1. Gather all DV's into a single column
2. Create separate variables that identify the trial and outcome
3. Spread outcomes into individual rows
4. Arrange dataframe by subject id and outcome
```{r}
DF.long <- DF %>%
  # (1)
  gather(key = "dv", value = "value",
         happ1_emot_hap : neut2_supp_con
         ) %>%
  # (2)
  separate(col = "dv", into = c("trial", "outcome"),
           sep = "_...._") %>%  # variable naming convention contains this seperator
  # (3)
  spread(key = "outcome", value = "value") %>%
  # (4)
  arrange(exper_ssid_var, trial)
```

#### Long-format: calculate happiness and anger ratings
Calculate happiness and anger ratings
```{r}
DF.long %<>%
  rowwise() %>%
  mutate(anger = mean(c(agg, irr, ann)),
         happy = mean(c(hap, sat, enj))
         ) %>% 
  ungroup()
```

#### Long-format: clean dataframe
Calculate a block # variable
```{r}
DF.long %<>%
  mutate(block.num = if_else(condition = trial == "angr1" |
                                         trial == "happ1" |
                                         trial == "neut1",
                             true = 1,
                             false = 2))
```

Now that we have a variable that indicates what block the trial was, we can create a new trial variable that removes the redundant information abuot block
```{r}
DF.long$trial <- as.factor(
  gsub('.$', '', DF.long$trial))
```

Organize long dataframe
```{r}
DF.long %<>%
  select(# subject-level variables
          exper_init_var, exper_ssid_var, demand,
          feedb_awar_var, feedb_blef_var, video_awar_var,
          heard_awar_var,
          
          # block variables
          block.num,
          
          # trial-level variables
          trial, anger, happy,
          hap, sat, enj,
          agg, irr, ann, dif)
```

Delete original dataframe
```{r}
rm(DF)
```

Export cleaned dataframes
```{r eval = FALSE}
write.csv(x = DF.wide, 
          file = "demandy19a_data_wide_clean.csv")

write.csv(x = DF.long,
          file = "demandy19a_data_long_clean.csv")
```

## Explore dataset
### Demographics
```{r}
DF.wide$indiv_gend_var <- as.factor(DF.wide$indiv_gend_var)

# calculate proportion of women and men
DF.wide %>% 
  group_by(indiv_gend_var) %>% 
  summarise(no_rows = length(indiv_gend_var))

# calculate age descriptives
DF.wide %>% 
  summarise(mean = mean(indiv_agee_var),
            sd = sd(indiv_agee_var))
```

### Emotion responses
#### Individual items
##### Histograms
Create histogram for each happiness item
```{r}
emo.hist <- list()

for (emo in c("hap", "sat", "enj")){
  emo.hist[[emo]] <- 
    ggplot(DF.long, 
           aes_string(x = emo,
                      fill = "trial")) +
    geom_histogram(binwidth = 1, 
                   alpha= .6, 
                   position= "identity") +
    ylim(0, 500) +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())
}

# grid.arrange
grid.arrange(emo.hist$hap, emo.hist$sat, emo.hist$enj,
             top = "Individual happiness item reports after each trial")

# delete vestigial
rm(emo, emo.hist)
```

Create histogram for each anger item
```{r}
emo.hist <- list()

for (emo in c("agg", "ann", "irr")){
  emo.hist[[emo]] <- 
    ggplot(DF.long, 
           aes_string(x = emo,
                      fill = "trial")) +
    geom_histogram(binwidth = 1, 
                   alpha= .6, 
                   position= "identity") +
    ylim(0, 500) +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())
}

# grid.arrange
grid.arrange(emo.hist$agg, emo.hist$ann, emo.hist$irr,
             top = "Individual anger item reports reports after each trial")

# delete vestigial
rm(emo, emo.hist)
```

##### Internal reliability
Since participants provide reports for the emotion items six times (three trials * two blocks), we will examine their correlations seperately for each trial and block.
```{r}
# create a blank dataframe to paste results in
alpha.DF <- data.frame(block.num = factor(), 
                       trial = factor(), 
                       alpha.h = numeric(),
                       alpha.a = numeric())

# loop through each trial and block and calculate alpha for the happiness and anger scores
for (trial in unique(DF.long$trial)){
  for (block.num in unique(DF.long$block.num)) {
    # happy items alpha
    alpha.h <-
      DF.long[DF.long$trial == trial & 
          DF.long$block.num == block.num, ] %>%
      select(hap, sat, enj) %>%
      alpha()
      
    # anger items alpha  
    alpha.a <-
      DF.long[DF.long$trial == trial & 
          DF.long$block.num == block.num, ] %>% 
      select(agg, irr, ann) %>%
      alpha()
    
    # save results to dataframe
    alpha.DF <- rbind(alpha.DF,
                      cbind(block.num = block.num,
                            trial = trial,
                            alpha.h = alpha.h[["total"]][["raw_alpha"]],
                            alpha.a = alpha.a[["total"]][["raw_alpha"]]
                            )
                      )
  }
}

# View reliability for every trial and block combination
## View(alpha.DF)

# calculate reliability for happiness and anger items overall
alpha.DF %>% 
  mutate(alpha.h = as.numeric(as.character(alpha.h)),
         alpha.a = as.numeric(as.character(alpha.a))
         ) %>% 
  summarise(alpha.h.avg = mean(alpha.h),
            alpha.a.avg = mean(alpha.a))

# delete vestigial
rm(alpha.a, alpha.DF, alpha.h, block.num, trial)
```

```{r warning = FALSE}
# happy items (alpha = .92)
DF.long %>%
  select(hap, sat, enj) %>%
  alpha()

# anger items (alpha = .89)
DF.long %>%
  select(agg, irr, ann) %>%
  alpha()

# delete individual emotion items
DF.long %<>%
  select(-c(hap : ann))
```

### Emotion scales
#### Happiness density plot
```{r}
ggplot(DF.long, aes(x = happy, fill = trial)) +
  geom_density(alpha = .6,
               adjust = 3) +
  labs(title = "Happy reports after each pose") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

#### Anger density plot
```{r}
ggplot(DF.long, aes(x = anger, fill = trial)) +
  geom_density(alpha = .6,
               adjust = 10) +
  labs(title = "Anger reports after each pose") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

## Manipulation checks
### Aware of ffh
Visualize distributions
```{r}
ggplot(DF.long, aes(x = feedb_awar_var, fill = demand)) +
  geom_density(alpha = .6,
               adjust = 1.5) +
  labs(title = "Awareness of our interest in the ffh in each condition") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

Analyses
```{r}
# ANOVA
awar.aov <- aov(feedb_awar_var ~ demand,
              data = DF.wide)
summary(awar.aov)

# pairwise comparisons with unadjusted p-values
emmeans(awar.aov, pairwise ~ demand,
        infer = c(TRUE, TRUE),
        adjust = "none")

# raw group Ms and SDs
DF.long %>%
  group_by(demand) %>%
  summarise(mean = mean(feedb_awar_var),
            sd = sd(feedb_awar_var))

rm(awar.aov)
```

### Belief in ffh
Visualize distributions
```{r}
ggplot(DF.long, aes(x = feedb_blef_var, fill = demand)) +
  geom_density(alpha = .6,
               adjust = 1.5) +
  labs(title = "Belief in the ffh in each condition") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

Analyses
```{r}
# ANOVA
blef.aov <- aov(feedb_blef_var ~ demand,
                data = DF.wide)
summary(blef.aov)

# pairwise comparisons with unadjusted p-values
emmeans(blef.aov, pairwise ~ demand,
        infer = c(TRUE, TRUE),
        adjust = "none")

# raw group Ms and SDs
DF.long %>%
  group_by(demand) %>%
  summarise(mean = mean(feedb_blef_var,
                        na.rm = TRUE),
            sd = sd(feedb_blef_var,
                    na.rm = TRUE))

rm(blef.aov)
```

## Confirmatory analyses
Convert subject id and block.num to a factor
```{r}
DF.long$exper_ssid_var <- as.factor(DF.long$exper_ssid_var)

DF.long$block.num <- as.factor(DF.long$block.num)
```

### Happiness scores
Full model. 

Note: model will not converge if random effects are included
```{r}
h.lmer.full <- lmer(happy ~ trial * demand * block.num +
                      (1 | exper_ssid_var),
                    data = DF.long)

summary(h.lmer.full)
anova(h.lmer.full)
```

Decompose main effects
```{r}
# trial
lsmeansLT(h.lmer.full, which =  "trial", pairwise = TRUE)

DF.long %>%
    group_by(trial) %>%
    summarise(mean = mean(happy),
              sd = sd(happy))

# demand
lsmeansLT(h.lmer.full, which =  "demand", pairwise = TRUE)

DF.long %>%
    group_by(demand) %>%
    summarise(mean = mean(happy),
              sd = sd(happy))

# block.num
lsmeansLT(h.lmer.full, which =  "block.num", pairwise = TRUE)

DF.long %>%
    group_by(block.num) %>%
    summarise(mean = mean(happy),
              sd = sd(happy))
```

Decompose trial:demand interaction
```{r}
joint_tests(h.lmer.full, by = "demand")

emmeans(h.lmer.full, pairwise ~ trial | demand,
        infer = c(TRUE, TRUE),
        adjust = "none")

DF.long %>%
    group_by(demand, trial) %>%
    summarise(mean = mean(happy),
              sd = sd(happy))
```

Decompose trial:block interaction
```{r}
joint_tests(h.lmer.full, by = "block.num")
```

```{r}
rm(h.lmer.full)
```

### Anger scores
Same model structure as happiness. Similar results if fully random model is fit.
```{r}
a.lmer.full <- lmer(anger ~ trial * demand * block.num +
                      (1 | exper_ssid_var),
                    data = DF.long)
summary(a.lmer.full)
anova(a.lmer.full)
```

Decompose main effects
```{r}
# trail effects
lsmeansLT(a.lmer.full, which =  "trial", pairwise = TRUE)

DF.long %>%
    group_by(trial) %>%
    summarise(mean = mean(anger),
              sd = sd(anger))

# demand effects
lsmeansLT(a.lmer.full, which =  "demand", pairwise = TRUE)

DF.long %>%
    group_by(demand) %>%
    summarise(mean = mean(anger),
              sd = sd(anger))

# block number effects
lsmeansLT(a.lmer.full, which =  "block.num", pairwise = TRUE)

DF.long %>%
    group_by(block.num) %>%
    summarise(mean = mean(anger),
              sd = sd(anger))
```

Decompose trial:demand effect
```{r}
joint_tests(a.lmer.full, by = "demand")

emmeans(a.lmer.full, pairwise ~ trial | demand,
        infer = c(TRUE, TRUE),
        adjust = "none")

DF.long %>%
    group_by(demand, trial) %>%
    summarise(mean = mean(anger),
              sd = sd(anger))
```

```{r}
rm(a.lmer.full)
```

### Figure 1
```{r}
# create a matrix of summary statistics
  ## happy self-reports
  smry.h <- DF.long %>%
    group_by(demand, trial) %>%
    summarise(mean = mean(happy),
              sd = sd(happy),
              n_obs = n(),
              se = sd(happy)/sqrt(n())
              )
  ## anger self-reports
  smry.a <- DF.long %>%
    group_by(demand, trial) %>%
    summarise(mean = mean(anger),
              sd = sd(anger),
              n_obs = n(),
              se = sd(anger)/sqrt(n())
              )

  ## combine matrices 
  smry <- rbind(cbind(dv = rep("Self-reported happiness", 9), 
                      smry.h),
                cbind(dv = rep("Self-reported anger", 9), 
                      smry.a)
                )
  rm(smry.a, smry.h)
  
  ## re-order and re-name facets
  smry$dv <- factor(smry$dv,
                    levels = c("Self-reported happiness",
                               "Self-reported anger"))
  
  smry$trial <- factor(smry$trial, 
                       levels = c("happ", "neut","angr"))
  levels(smry$trial)[levels(smry$trial)=="happ"] <- "happy"
  levels(smry$trial)[levels(smry$trial)=="neut"] <- "neutral"
  levels(smry$trial)[levels(smry$trial)=="angr"] <- "angry"
  
  smry$demand <- factor(smry$demand, 
                        levels = c("pos", "neu","neg"))
  levels(smry$demand)[levels(smry$demand)=="pos"] <- 
    "positive expectation"
  levels(smry$demand)[levels(smry$demand)=="neu"] <- 
    "control"
  levels(smry$demand)[levels(smry$demand)=="neg"] <- 
    "null expectation"
  
# plot
ggplot(smry, aes(trial, mean)) +
  facet_grid(dv ~ demand, switch = "y", 
             scales = "free_x") +
  geom_col(width = .80, fill = "grey69", colour = "black") +
  geom_errorbar(aes(ymin = mean - se,
                    ymax = mean + se,
                    width = 0.2)) +
  labs(y = NULL, x = "Facial expression pose") +
  ylim(0, 2) +
  theme_classic() +
  theme(strip.placement = "outside",
        strip.background.y = element_blank(),
        #strip.background.x = element_blank(),
        #strip.background.x = element_rect(colour = "black",
        #                                  fill = "white"),
        strip.text.y = element_text(size = 10),
        axis.title.x.bottom = element_text(size = 10))

rm(smry)
```

## Exploratory analysesc
### Examine whether difficulty varied by trial and block
Note: models will not converge with random slopes
```{r}
d.lmer.full <- lmer(dif ~ trial * demand * block.num +
                      (1 | exper_ssid_var),
                    data = DF.long)
summary(d.lmer.full)
anova(d.lmer.full)

# decompose trial effect
lsmeansLT(d.lmer.full, which =  "trial", pairwise = TRUE)

DF.long %>%
    group_by(trial) %>%
    summarise(mean = mean(dif),
              sd = sd(dif))

# decompose demand effect
lsmeansLT(d.lmer.full, which =  "demand", pairwise = TRUE)

DF.long %>%
    group_by(demand) %>%
    summarise(mean = mean(dif),
              sd = sd(dif))
```

```{r}
rm(d.lmer.full)
```

#### Re-examine happy pose effects controlling for difficulty
```{r}
h.d.lmer.full <- lmer(happy ~ (dif + trial + demand + block.num 
                               + trial:demand) + (1 | exper_ssid_var),
                      data = DF.long)
summary(h.d.lmer.full)
anova(h.d.lmer.full)
```

Decompose trial * demand effect
```{r}
joint_tests(h.d.lmer.full, by = "demand")

emmeans(h.d.lmer.full, pairwise ~ trial | demand,
        infer = c(TRUE, TRUE),
        adjust = "none")
```

```{r}
rm(h.d.lmer.full)
```

#### Re-examine anger pose effects controlling for difficulty
```{r}
a.d.lmer.full <- lmer(anger ~ (dif + trial + demand + block.num 
                               + trial:demand) + (1 | exper_ssid_var),
                      data = DF.long)
summary(a.d.lmer.full)
anova(a.d.lmer.full)
```

Decompose trial * demand effect
```{r}
joint_tests(a.d.lmer.full, by = "demand")

emmeans(a.d.lmer.full, pairwise ~ trial | demand,
        infer = c(TRUE, TRUE),
        adjust = "none")
```

```{r}
rm(a.d.lmer.full)
```

### Examine whether facial feedback effects are moderated by belief in the facial feedback hypothesis
```{r}
b.h.lmer <- lmer(happy ~ (trial + feedb_blef_var + block.num 
                        + trial:feedb_blef_var) + (1 | exper_ssid_var),
               data = DF.long)
summary(b.h.lmer)
anova(b.h.lmer)

b.a.lmer <- lmer(anger ~ (trial + feedb_blef_var + block.num 
                        + trial:feedb_blef_var) + (1 | exper_ssid_var),
               data = DF.long)
summary(b.a.lmer)
anova(b.a.lmer)

rm(b.h.lmer, b.a.lmer)
```

To decompose this interaction, make belief a high and low factor
```{r}
DF.long %<>% 
  mutate(feedb_blef_nom = if_else(condition = feedb_blef_var > 2.15,
                                  true = "high",
                                  false = "low",
                                  missing = NULL),
         feedb_blef_nom = as.factor(feedb_blef_nom))
```

Re-fit models and decompose interaction
```{r}
b.h.lmer <- lmer(happy ~ (trial + feedb_blef_nom + block.num 
                        + trial:feedb_blef_nom) + (1 | exper_ssid_var),
               data = DF.long)
summary(b.h.lmer)
anova(b.h.lmer)

# decompose trial by belief interaction
joint_tests(b.h.lmer, by = "feedb_blef_nom")

# delete vestigial
rm(b.h.lmer)
```

```{r}
b.a.lmer <- lmer(anger ~ (trial + feedb_blef_nom + block.num 
                        + trial:feedb_blef_nom) + (1 | exper_ssid_var),
               data = DF.long)
summary(b.a.lmer)
anova(b.a.lmer)

# decompose trial by belief interaction
joint_tests(b.a.lmer, by = "feedb_blef_nom")

# delete vestigial
rm(b.a.lmer)
```

## Calculate effect sizes
To quantify the size of the pose effect in the positive expectation, control, and null expectations conditions, standardized mean difference scores were computed (Cohen’s drm; Cohen, 1988). For ease of comprehension, self-reported emotional experience was averaged across block and effect sizes were calculated as the mean difference between (a) the emotion-congruent pose and (b) the average of the emotion-incongruent poses. For example, to calculate the size of the effect of pose on happiness, we compared happiness scores between (a) the average of the two happy pose trials, and (b) the average of the two neutral pose and two angry pose trials.

### Prep dataframe
Create new dataframe
```{r}
DF.w.es <- DF.wide
```

Average across blocks
```{r}
DF.w.es <- DF.w.es %>%
  rowwise() %>%
  mutate(# happy trial ratings
         happ.happy = mean(c(happ1.happy,
                             happ2.happy)),
         happ.anger = mean(c(happ1.anger,
                             happ2.anger)),
         
         # angry trial ratings
         angr.happy = mean(c(angr1.happy,
                             angr2.happy)),
         angr.anger = mean(c(angr1.anger,
                             angr2.anger)),
         
         # neutral trial ratings
         neut.happy = mean(c(neut1.happy,
                             neut2.happy)),
         neut.anger = mean(c(neut1.anger,
                             neut2.anger))
  ) %>%
  ungroup() %>% 
  # delete vestigial
  select(-c(happ1.happy : neut2.anger))
```

Average across non-target trials
```{r}
DF.w.es <- DF.w.es %>%
  rowwise() %>% 
  mutate(# happiness scores for non-target trials (angr and neut)
         angrneut.happy = mean(c(angr.happy, neut.happy)),
         
         # anger scores for non-target trials (happ and neut)
         happneut.anger = mean(c(happ.anger, neut.anger))
         ) %>% 
  ungroup() %>% 
  # delete vestigial
  select(-c(angr.happy, neut.happy, happ.anger, neut.anger))
```

Pivot longer
```{r}
tmp <- DF.w.es %>% 
  pivot_longer(cols = c(happ.happy, angrneut.happy),
                names_to = "group",
                values_to = "happiness") %>% 
  select(exper_ssid_var, demand, group, happiness)

tmp.dp <- tmp %>% 
  filter(demand == "pos")

cohen.d(formula = happiness ~ group | Subject(exper_ssid_var),
        data = tmp.dp,
        paired = TRUE,
        within = TRUE)

rm(tmp, tmp.dp)
```

Calculate difference between target and non-target trials
```{r eval = FALSE}
DF.w.es <- DF.w.es %>% 
  rowwise() %>% 
  mutate(# happiness facial feedback effect
         happy.diff = happ.happy - angrneut.happy,
         
         # anger facial feedback effect
         anger.diff = angr.anger - happneut.anger) %>% 
  ungroup()
```

```{r}
# formula: Cooper, Hedges, & Valentine, 2009; p. 229
EsWitnMeanDiff <- function(m.diff, sd.diff, corr){
  es <- (m.diff / sd.diff) * sqrt(2 * (1- corr));
  return(es)
}
```

#### Happy facial feedback effects
Demand positive
```{r}
DF.w.pos.es <- DF.w.es %>%
  filter(demand == "pos")



# d = 1.19
EsWitnMeanDiff(m.diff = mean(DF.w.pos.es$happy.diff),
               sd.diff = sd(DF.w.pos.es$happy.diff),
               corr = cor(DF.w.pos.es$happ.happy,
                          DF.w.pos.es$angrneut.happy)
               )

rm(DF.w.pos.es)
```

Demand neutral
```{r}
DF.w.neu.es <- DF.w.es %>%
  filter(demand == "neu")

# d = 0.92
EsWitnMeanDiff(m.diff = mean(DF.w.neu.es$happy.diff),
               sd.diff = sd(DF.w.neu.es$happy.diff),
               corr = cor(DF.w.neu.es$happ.happy,
                          DF.w.neu.es$angrneut.happy)
               )

rm(DF.w.neu.es)
```

Demand negative
```{r}
DF.w.neg.es <- DF.w.es %>%
  filter(demand == "neg")

# d = 0.51
EsWitnMeanDiff(m.diff = mean(DF.w.neg.es$happy.diff),
               sd.diff = sd(DF.w.neg.es$happy.diff),
               corr = cor(DF.w.neg.es$happ.happy,
                          DF.w.neg.es$angrneut.happy)
               )

rm(DF.w.neg.es)
```

#### Anger facial feedback effects
Demand positive
```{r}
DF.w.pos.es <- DF.w.es %>%
  filter(demand == "pos")

# d = 0.75
EsWitnMeanDiff(m.diff = mean(DF.w.pos.es$anger.diff),
               sd.diff = sd(DF.w.pos.es$anger.diff),
               corr = cor(DF.w.pos.es$angr.anger,
                          DF.w.pos.es$happneut.anger)
               )

rm(DF.w.pos.es)
```

Demand neutral
```{r}
DF.w.neu.es <- DF.w.es %>%
  filter(demand == "neu")

# d = 0.69
EsWitnMeanDiff(m.diff = mean(DF.w.neu.es$anger.diff),
               sd.diff = sd(DF.w.neu.es$anger.diff),
               corr = cor(DF.w.neu.es$angr.anger,
                          DF.w.neu.es$happneut.anger)
               )

rm(DF.w.neu.es)
```

Demand negative
```{r}
DF.w.neg.es <- DF.w.es %>%
  filter(demand == "neg")

# d = 0.34
EsWitnMeanDiff(m.diff = mean(DF.w.neg.es$anger.diff),
               sd.diff = sd(DF.w.neg.es$anger.diff),
               corr = cor(DF.w.neg.es$angr.anger,
                          DF.w.neg.es$happneut.anger)
               )

rm(DF.w.neg.es, EsWitnMeanDiff)
```
